Prestige as a Driving Force in Cultural Transmission

### 2022-04-04 ms/PrestigeBias.tex
results validation; figures; discussion

We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}.

Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias/blob/master/notebooks/Influence_model.ipynb}{this notebook}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{Approximations}
Our model is defined by two nested stochastic processes. Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}. Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two approximations such processes, summarized here and explained in detail below:
\begin{enumerate}
\item 
The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value. 
\end{enumerate}
\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers. 
Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
\end{enumerate}

@@

\paragraph{Numerical validation.}
To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations.
We executed varying amount of simulations of our original model to compute an observed distribution of number of copiers from the average empirical distribution.The number of simulation required depended on the parameters used. To compare the observed distribution with the expected DM distribution, we use a Pearson's chi-squared test of goodness-of-fit to reject or accept the null hypothesis that the simulation results are drawn from a DM distribution.

When testing multiple values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.

For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required. % TODO did you test other distributions?
% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % remove legend
  % change y labels: "Fixation probability" "Fixation time"
  % change x label: "Number of simulations"
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Model testing}

Here we examine the difference between the dichotomous trait model defined in \cref{eq:binary-model} and the Dirichlet-Multinomial approximation we presented in \cref{cor:dirichlet}. We focus on the fixation probability and fixation time of the advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$.

First, we find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1000$ (\Cref{fig:num_sims}).
Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions
First we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).

In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}.

@@

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_error} we see the comparison when heterogeneous estimation error is applied to both models. When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{Comparison of the DM approximation and the full model when success weight is heterogeneous. High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
	% TODO
	% see comments in previous figure
\end{figure}

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the estimation error comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

@@

After finding that the DM distribution is a good approximation of the role-model choice process we turn our attention to the evolutionary dynamics.
We focus on the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias, on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
For simplicity, we do not include estimation error in this analysis.
As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
\\

% TODO in the following, I would organize differently:
% 1.  remark for E[x'-x] the "drift" (1st order) coefficient in a diffusion equation approximation
% 2. result on effective selection coefficient
% 3. remark for V[x'-x] the "diffusion" (2nd order) coefficient in a diffusion equation approximation
% 4. result of effective population size
% 5. result for fixation prob
% 6. result for fixation time
% 7. result for changing environment

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size. The approximation seems very good, and is also condensed around the mathematical equation expectancy. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. The approximation seems good, and is also condensed around the mathematical equation expectancy. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

\subsection*{Changing environment}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

@@

We wanted again to validate our results, using simulations.
This time, the number of parameters increased: in addition to $\alpha,\beta$, there are also $k,l$ as model parameters.

We again tried different variations of the parameters, changing only one of them at a time.
In \cref{fig:ch_env_alpha_beta} we can see that $\alpha$ on its own does not cause any deviation for the the estimation. $\beta$ however affects the results greatly.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{success bias/selection coefficient is: $1-\beta=s=0.005$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{success weight is: $\alpha=0.1$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients. Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values. High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$.}
  \label{fig:ch_env_alpha_beta}
\end{figure}

We plotted along the modified estimation the original Kimura's estimation, as a limiter. We suspect that when $\beta$ is too large, there won't be many cycles in the simulations. This might happen if either the population reaches a high frequency of the ideal trait after only a few cycles, or it get extinct very quickly, because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in a fast extinction.

In the larger values of $beta$ we even see a deviation from the original estimation environment, but it's to be expected, because Kimura's equations are only viable for small $s$ values.

We then also tried changing the composition of the cycle, by keeping a constant $n=40$, but changing $k,l$ accordingly.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle. When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}

In \cref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
When using higher values of $n$, the simulation results doesn't fit the equation result as with lower values. This is due to the fact that our proof, and therefore our equation is more accurate when more cycles occur. When $n$ is high, there will be less cycles, and the simulations will get closer to the constant environment equation.

\section*{Discussion}
\subsection*{summary}
Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
Some cultural traits can be more likely to be copied by others, regardless of their frequency in the population.  
Such transmission biases are common in cultural transmission processes. 
Many models are based on the assumption that success can be correctly identified, and easily copied.
Here we assume that success isn't correctly identified, therefore individuals may use other indicators to try and estimate the success of potential role-models.
We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success accurately is harder.
\textbf{We investigated the effects of prestige on a population:} we studied the behavior of an invading trait, analyzed its dynamics mathematically, and extended the basic constant environment to a changing one.
We believe prestige is composed of two main components: a trait that indicates success (but doesn't guarantee it), and the influence the individual already has on others, i.e number of individuals already chose him as a role-model.
We suggest a model for \textit{prestige bias}, inspired by the model \citet{evolutionBook} have suggested, and added the \textit{influence bias} to it.
\textbf{We approximated our models using various distributions, and compared them to the original model using simulations.}
We showed that a \textit{Rich getting richer} type of model can be approximated well by the general binomial distribution and the dirichlet multinomial distribution.
We experimented with constant and changing environment in our model, and created a variation of a binary model for easier mathematical and computational analysis.
We believe that in this era of social media it is easy to estimate one's influence over others.
It is therefore crucial to model the cultural biases more realistically than success bias based model, and we believe including influence is crucial for that purpose.\\
\textbf{With a more realistic model of a common cultural transmission bias, we may be able to better understand decision-making processes in humans, including life-changing choices such as occupation or a life partner.} 
Our model can be expanded in multiple ways: observing the effects of different bias functions, including errors in estimating the influence, combining factors of cost when copying from an influential role model (not all could afford to copy from the most popular role-model), and analyzing the differences when including several optimal values for the indicator trait (multiple preference traits in the population).

\subsection*{Prestige in the literature}
So far we discussed prestige as a main bias in humans, and to some extent in non-human species. Here we further base our claims and present additional appearances of prestige in nature and in the literature. \\

>>>>

We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{Approximations}
Our model is defined by two nested stochastic processes. Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}. Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two such approximations, summarized here and explained in detail below:
\begin{enumerate}
\item 
The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value. 
\end{enumerate}
\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers. 
Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
\end{enumerate}

@@

\paragraph{Numerical validation.}
To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
We then compared this observed distribution with the expected theoretical DM distribution using Pearson's chi-squared test of goodness-of-fit. Thus, we can reject or accept the null hypothesis that simulation results are effectively drawn from a DM distribution.

Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
For high $\alpha$ values (above 0.5), very few simulations were needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$).
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required. % TODO did you test other distributions?
% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

Next, we examined the fixation probability and fixation time of an advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$). 
%In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}. % TODO do we need this sentence?
When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(X,X)$. % TODO replace X and X with relevant symbols
We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % remove legend
  % change y labels: "Fixation probability" "Fixation time"
  % change x label: "Number of simulations"
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
	% TODO
	% see comments in previous figure
\end{figure}

@@

After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
For simplicity, we do not include estimation error in this analysis.
As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?

% TODO in the following, I would organize differently:
% 1.  remark for E[x'-x] the "drift" (1st order) coefficient in a diffusion equation approximation
% 2. result on effective selection coefficient
% 3. remark for V[x'-x] the "diffusion" (2nd order) coefficient in a diffusion equation approximation
% 4. result of effective population size
% 5. result for fixation prob
% 6. result for fixation time
% 7. result for changing environment
% so I didn't read the rest of the results very carefully, waiting for you to think about the re-arrangement suggestion first.

@@

\begin{figure}[h]
  \begin{center}
    %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
  Error bars show mean and 95\% confidence intervals.
  Effective population, $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  \label{fig:var_alpha}
  % TODO
  % - better x and y label, as noted above
  % - in legend, replace "kimura" with "Approx."
  % - in legend, remove "=2s"
  % - change approximation color, it is too similar to WF simulations
  % - make the horizontal line black?
  % - caption should start with bold sentence summarizing the figure. 
  % - in caption add description of each parameter (as I did for N)
  %
\end{figure}

\begin{figure}[h]
  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  % TODO 
  % - see previous figure
  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
  % - consider using plt.xscale('log')
  % - maybe you can merge this figure with the figure?
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

\paragraph{Changing environment.}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

@@

\begin{figure}[h]
  \begin{center}
  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{subfigure}{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients. Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values. High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success weight is: $\alpha=0.1$. 
  }
  % TODO 
  % see previous figures..
  % not sure you need the green curve in the left panel
  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
  % 
  \label{fig:ch_env_alpha_beta}
\end{figure}

We validate our results using simulations.
We find that $\alpha$ does not have a significant effect on the approximations (\cref{fig:ch_env_alpha_beta}).
However, $\beta$ does. 
We plotted along the modified estimation the original Kimura's estimation, as a limiter. % TODO rephrase, this sentence is not clear at all
We suspect that when $\beta$ is too large, there won't be many cycles in the simulations. This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or it get extinct very quickly, % TODO what gets extinct? what does "it" refers to?
 because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in fast extinction. % TODO read and rephrase.
For lower % TODO this was "higher" but should be "lower" right?
values of $\beta$ we see a deviation from the original estimation environment, % TODO what is "estimation environment"?
but it's to be expected, because Kimura's equations weak fitness (i.e., low selection coefficients, $s$).

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  %TODO add panel labels (a) and (b) on figures corner.
  % see previous figures todos
  % move legend to upper left? it is currently hiding something
  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle. % TODO reminder what k and l are.
   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}

We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
We found that larger $k$-to-$l$ ratio increases the agreement between the modified equation and the original estimation of the constant environment. % "modified....environment" unclear.
When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
This is because our approximation is more precise when more cycles occur.
When $n$ is high, there will be less cycles, % TODO why higher n gives less cycles?
and the simulations will get closer to the constant environment equation.

% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
\paragraph{Summary.}
During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other indicator.

Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers. We found approximations for the role-model choice process: the generalized binomial distribution that approximates the number of copiers of a single role-model, and the Dirichlet-Multinomial distribution that approximates the distribution of copiers in the entire population in a \textit{rich-getting-richer} type of process. 
We then studied the effects of prestige bias on the fixation probability and time of an invading advantageous cultural phenotype in both a constant and a changing environment.
% TODO what did we find?

\paragraph{Prestige in the literature.}

According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches. They found that leadership is mostly observed when there is a profound social network in the group, % TODO profound sounds weird here. what do you mean by it?
and when there are individuals that present leadership behavior.
Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
When no individual posseses such traits, or when the social network is lacking, % TODO lacking what?
decisions are more likely to be made by consensus.
Leader may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
In some cases, %e.g. fish, % TODO ref for fish? otherwise don't mention fish
 the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
However, leadership may also carry selection benefits. For example, given the route to the foraging site was successful, the leader and his closest followers would gain most or the best of the food, whereas in consensus decision making, the food would be shared more equally. Or, sexual selection may also provide a selection benefit advantage to leaders, who might gain more sexual partners due to their leadership of the group. \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
They show that leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose. % TODO are you sure? this is in baboons?

In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. However, wrong decision making that harms the group could result in harm.
In modern society it is less common to worry about mere survival, and so the prestigious positions, even though they are not without risks and costs, are not as dangerous as for animals in nature. % TODO reference? I'm not sure this is correct
This may be the reason humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them. % you give two reasons - "this may be the reason" and "as they may reap..." I think the latter is more correct. also I think it is personality and family driven, to an extent.
This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive. % TODO I'm not sure, let's discuss!
